\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2021-04-27 analysis/paper/paper.Rmd
added ref and summary of the PFT labeling process

>>>>

We manually added plant functional type (PFT) along with additional morphological and taxonomic labels to the spectra. We used the [USDA Plants Database](https://plants.sc.egov.usda.gov/) to identify each taxon's phenology (evergreen or deciduous), leaf type (needleleaf or broadleaf), and taxonomic family classification. We used the NEON Woody Vegetation Structure data to determine the growth form (shrub or tree) most commonly assigned to each taxon class, since some taxa can exist as trees or shrubs. The PFT labels were inspired by the MODIS Land Cover classes [@cover1999modis]: evergreen needleleaf forest, evergreen broadleaf forest, deciduous needleleaf forest, deciduous broadleaf forest, shrub, grass, and bare ground.
